---
title       : Spherical Calculations
subtitle    : 
author      : James D'Amato
job         : Analytics Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Spherical Calculations

Based on the user's input of a radius through the API, the Shiny App will calculate the following attributes of a sphere:
* Diameter
* Volume
* Surface Area

The Shiny App will also repeat the radius that the user entered in the results pane

---

## Diameter Calculation

The Shiny App calculates the diameter using the following formula:
* Diameter = 2r
E.g if the radius is 2, then the diameter is:
```{r}
2 * 2
```

---

## Volume Calculation

The Shiny App also calculates the volume of a sphere using the following formula:
* Volume = (4/3) pi r ^ 3
E.g. if the radius is 2, then the volume of the sphere is:
```{r}
(4/3)*pi*2^3
```

---

## Surface Area Calculation

Lastly, the Shiny App calculates the surface area of a sphere using the following formula:
* Surface Area = 4 pi r ^ 3
E.g. if the radius of the sphere is 2, then the surface area of the sphere is:
```{r}
4 * pi * 2 ^ 3
```



